RationalGRL: A Framework for Argumentation and Goal Modeling

### 2018-05-03 discussion.tex
validation

\paragraph{Beliefs in GRL and Belief Revision} As mentioned already in the introduction, it is possible in GRL to rationalize models
through so-called \emph{belief} elements. These beliefs are elements that can be attached to an IE with a \emph{belief link}. The content of a belief is a textual description, which can explain, for instance, the rationale for including an IE in the resulting goal model. There are several important differences between GRL beliefs and RationalGRL arguments.

>>>>

\paragraph{Beliefs in GRL} As mentioned already in the introduction, it is possible in GRL to rationalize models
through so-called \emph{belief} elements. These beliefs are elements that can be attached to an IE with a \emph{belief link}. The content of a belief is a textual description, which can explain, for instance, the rationale for including an IE in the resulting goal model. There are several important differences between GRL beliefs and RationalGRL arguments.

### 2018-05-03 validation.tex
validation

@@

\todo{marcvanzee}{marcvanzee,floris}{This is copied from the CAiSE paper where we did the original evaluation with two Enterprise Architects. I'm not sure if we can re-use it. The main problem is that at that time we developed GRL models specifically for the organization in which the Enterprise Architects were working, and we don't have such a model now. What do you think?}

@@

\subsection{Empirical evaluation}

\todo{marcvanzee}{marcvanzee,florisbex}{Write this}

>>>>

\subsection{RationalGRL user evaluation}

Since RationalGRL is targeted at practitioners and not just for academic end users, we performed a brief user evaluation with 20 users. In this evaluation, we asked participants to rate and comment the usability of the RationalGRL tool. The study consisted of three parts:
\begin{enumerate}
\item Explanation: We explained the participants the basics of the RationalGRL methodology and the RationalGRL tool in a document we wrote.
\item Modelling: We asked the participants to model a summarized discussion in the RationalGRL tool.
\item Questionnaire: We asked some questions about the usability of the RationalGRL tool, and how it relates to GRL.
\end{enumerate}

The instructions for these three parts were contained in a single document that we sent out to the participants.\footnote{See \url{www.rationalgrl.com}, page ``Empirical Study''} At the end of the document we provided a link to the survey\footnote{https://goo.gl/forms/fDSMUnAV20wy7kbY2}.

In the second task, the users were asked to visit rationalgrl.com, where they could start experimenting with the RationalGRL tool directly. We presented the users with summarized transcripts of the discussion about the development of the Traffic Controller, and then asked them to model this to the best of their abilities. ADD RESULTS HERE

For the third task, we asked the users to fill out a survey. The survey starts by asking about the users’ backgrounds. The participants turned out to have a relatively high level of experience with
IT, with an average rating of.... Experience
with goal modeling was less....

Explain rest of results here....

@@

\todo{marcvanzee}{marcvanzee,floris,sepideh}{This is copied from the CAiSE paper where we did the original evaluation with two Enterprise Architects. I'm not sure if we can re-use it. The main problem is that at that time we developed GRL models specifically for the organization in which the Enterprise Architects were working, and we don't have such a model now. What do you think?}

@@
